Probabilistic Model of Bilateral Lymphatic Spread in Head and Neck Cancer

### 2024-04-02 manuscript.qmd
add prevalences test plot

>>>>

## Prevalence Comparisons

Below we compare the predicted with the observed prevalence of some involvement patterns.

```{python}
#| echo: false
#| label: fig-prevalences
#| fig-cap: Prevalences of different scenarios.

from pathlib import Path

import matplotlib.pyplot as plt
from lymph import models
from lyscripts import utils
from lyscripts.scenario import Scenario
from lyscripts.plot.utils import draw, BetaPosterior, Histogram, COLOR_CYCLE

model_dir = Path("models/midline")
filename = model_dir / "prevalences.hdf5"

params = utils.load_yaml_params(model_dir / "params.yaml")
model = utils.create_model(params)
scenarios_config = utils.load_yaml_params("scenarios.yaml")
scenarios = Scenario.list_from_params(
  params=scenarios_config,
  is_uni=isinstance(model, models.Unilateral),
  side=params["model"].get("side", "ipsi")
)

fig, ax = plt.subplots()

content = []
color = next(COLOR_CYCLE)
content += [
  Histogram.from_hdf5(
    filename=filename,
    dataname=scenarios[0].md5_hash("prevalences"),
    color=color,
  ),
  BetaPosterior.from_hdf5(
    filename=filename,
    dataname=scenarios[0].md5_hash("prevalences"),
  ),
]
color = next(COLOR_CYCLE)
content += [
  Histogram.from_hdf5(
    filename=filename,
    dataname=scenarios[1].md5_hash("prevalences"),
    color=color,
  ),
  BetaPosterior.from_hdf5(
    filename=filename,
    dataname=scenarios[1].md5_hash("prevalences"),
  ),
]
draw(
  axes=ax,
  contents=content,
  percent_lims=(2., 2.),
)

```
